%-------------------------
% Resume in Latex
% Based on the sb2nov / jakegut resume template structure
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\setlength{\multicolsep}{0pt}
\input{glyphtounicode}

\definecolor{bulletblue}{RGB}{0,0,180}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{4.5pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.65in}
\addtolength{\textheight}{1.3in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Ensure PDF text stays machine-readable for ATS parsers (ligatures don't break on copy/extract)
\pdfgentounicode=1

% Sections formatting -- consistent gap ABOVE every heading, and a single
% controlled gap BELOW the rule (sectiongap), so every section starts
% the same visual distance from the rule.
\titlespacing*{\section}{0pt}{4pt}{2pt}
\titleformat{\section}{
  \scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule]

% Single uniform spacing constant applied directly after every \section heading
% (kept at 0pt now that titlespacing handles the gap below the rule)
\newcommand{\sectiongap}{\vspace{0pt}}

%-------------------------
% Custom commands
% Single uniform spacing constant used after every entry/bullet, everywhere
\newcommand{\itemgap}{\vspace{2pt}}

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2}
  }
}

\newcommand{\resumeItemPlain}[1]{
  \item\small{#1}
}

\newcommand{\resumeSubheading}[4]{
  \item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\[-2pt]
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{0pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}}

% Project entry: title on its own line, description starts on the next line
\newcommand{\resumeProjectItem}[2]{
  \item\small{
    \textbf{#1}\\[2pt]
    #2}
}

% Compact variants for lower-priority sections (Skills, Certifications, Activities)
\newcommand{\resumeCompactItem}[2]{
  \item\small{\textbf{#1}{: #2}}
}
\newcommand{\resumeCompactPlain}[1]{
  \item\small{#1}
}
\setlength{\parskip}{0pt}

\renewcommand{\labelitemii}{$\circ$}

% Uniform vertical rhythm: every list (experience, projects, education,
% activities) uses the same itemsep/parsep/topsep so gaps between entries
% match exactly across sections.
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, itemsep=4pt, parsep=0pt, topsep=1pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=1pt, parsep=0pt, topsep=1pt, leftmargin=18pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{1pt}}

% Blue-bullet list style for Skills / Certifications -- same itemize family, same spacing
\newenvironment{bulletcol}{
  \begin{itemize}[leftmargin=14pt, label={\color{bulletblue}\textbullet}, itemsep=2pt, topsep=1pt, parsep=0pt]
}{
  \end{itemize}
}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Firstname Lastname} & Email: \href{mailto:example@example.com}{example@example.com} \\[1pt]
  Full Stack Developer & Mobile: +1-234-567-8900 \\[1pt]
  GitHub: \href{https://github.com/example}{github.com/example} & LinkedIn: \href{https://linkedin.com/in/example}{linkedin.com/in/example} \\
\end{tabular*}
\vspace{-2pt}

%-----------SUMMARY-----------------
\section{Summary}
\resumeSubHeadingListStart
  \resumeItemPlain{Full Stack Developer with a Computer Science (AI \& Data Science) background, focused on building complete web applications end to end -- responsive frontends with HTML, CSS, and JavaScript/React, backed by Flask APIs and Firebase/SQL data layers, shown across 3 independently built projects. Brings added strength in data analysis from a Data Science internship.}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {SmartBridge}{Remote}
    {Data Science Intern}{2025}
    \resumeItemListStart
      \resumeItem{Data Analysis}
        {Analyzed and visualized datasets using Python, SQL, and Tableau as part of a structured data science internship program.}
      \resumeItem{Data Cleaning}
        {Cleaned and processed raw survey and tabular datasets, resolving missing values and inconsistent formatting to improve data quality for downstream analysis.}
      \resumeItem{Dashboards}
        {Designed 3+ interactive Tableau dashboards and data stories to support data-driven decision-making for stakeholder review.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
  \resumeProjectItem{AgriVision -- Crop Recommendation System}
    {Full-stack ML web application that recommends crops based on soil and weather inputs; trained the prediction model with scikit-learn, built a Flask backend serving inference APIs, and integrated frontend forms for user interaction. Built during Smart India Hackathon (Internal Round).}
  \resumeProjectItem{College Food Choices -- Data Visualization (Tableau)}
    {Cleaned and analyzed a college dietary survey dataset using Python and SQL, then built interactive Tableau dashboards surfacing food, health, and lifestyle trends across the student population.}
  \resumeProjectItem{RepoLogic -- GitHub Repository Analyzer}
    {AI-powered web application that explains public GitHub repositories using Retrieval-Augmented Generation (RAG) with the Gemini API; lets users select code or ask natural-language questions and returns explanations with file and line references.}
\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\begin{itemize}[leftmargin=*, itemsep=2pt, parsep=0pt, topsep=1pt]
  \resumeSubheading
    {University Name}{City, Country}
    {B.Tech in CSE (AI \& Data Science); CGPA: 8.8}{2023 -- 2027}
  \resumeSubheading
    {Junior College}{City, Country}
    {Intermediate (MPC); 85\%}{2021 -- 2023}
  \resumeSubheading
    {High School}{City, Country}
    {SSC; 88\%}{2021}
\end{itemize}

%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
\begin{multicols}{2}
\begin{bulletcol}
\small
\item \textbf{Languages:} Python, Java, JavaScript, SQL
\item \textbf{Frontend:} HTML, CSS, React
\item \textbf{Backend:} Flask, Node.js, Firebase
\item \textbf{Databases:} SQL, Firestore
\item \textbf{Data/ML Tools:} Pandas, NumPy, scikit-learn, Tableau, Excel
\item \textbf{Version Control:} Git, GitHub, VS Code, Jupyter Notebook
\end{bulletcol}
\end{multicols}

%-----------CERTIFICATIONS-----------------
\section{Certifications}
\begin{bulletcol}
\small
\item Programming in Java --- NPTEL (IIT Kharagpur)
\item Pandas \& NumPy --- Kaggle
\item Data Science Virtual Internship --- Altair
\item Web Full Stack Development --- EduSkills
\end{bulletcol}

%-----------ACTIVITIES-----------------
\section{Activities}
\resumeSubHeadingListStart
  \resumeCompactPlain{Participated in Smart India Hackathon (Internal Round) -- built the AgriVision project during the event.}
  \resumeCompactPlain{Open Source Contributor, GirlScript Summer of Code (GSSoC) 2026 -- contributed to open-source repositories via pull requests and issue resolution, gaining hands-on experience with documentation, the PR review process, and resolving merge conflicts.}
\resumeSubHeadingListEnd

\end{document}
